Spatial Reasoning and Statistical Graphics

### 2014-10-19 Paper/Draft1/TestingVisualAptitude.Rnw
References for VST

\caption{Comparison of scores from Iowa State students and scores reported in \citet{ekstrom1976manual}. Scaled scores are calculated based on information reported in the manual, scaled to account for differences in the number of questions answered during this experiment. Data shown are from the population most similar to ISU students, out of the data available.\label{tab:scorecomparison}}
\end{table}
\end{savenotes}

>>>>

\caption{Comparison of scores from Iowa State students and scores reported in \citet{ekstrom1976manual}. Scaled scores are calculated based on information reported in the manual, scaled to account for differences in the number of questions answered during this experiment. Data shown are from the population most similar to ISU students, out of the data available. The Visual Search task \citep{goldstein1973validity,demita1981validity,moerland1986neuropsychological} is not part of the Kit of Factor Referenced Cognitive Test data, and thus we do not have comparison data for the form used in this experiment. \label{tab:scorecomparison}}
\end{table}
\end{savenotes}
